Effective Reionization Likelihood from Planck 2018 Data (?)

### 2021-01-27 paper/rei.tex

\begin{figure}[ht]
\includegraphics[width=0.45\textwidth]{results/direct_mcmc/pl18_plots_zmax30/plot_pub_tau_gtz_dz_0p1_pl18_pc_zmax30_pliklite_post_0930_and_pl18_pc_zmax30_pliklite_srollv2_0930.pdf}
\caption{[placeholder] PC chains for zmax = 30. Planck 2018 srollv2 likelihood vs Planck 2015). [To be created and merged with the next plot as a single figure with two panels.]
}
\label{fig:plot_taugtz_2015_vs_2018}
\end{figure}

\begin{figure}[ht]
\includegraphics[width=0.45\textwidth]{results/direct_mcmc/pl18_plots_zmax30/plot_pub_tau_gtz_dz_0p1_pl18_pc_zmax30_pliklite_post_0930_and_pl18_pc_zmax30_pliklite_srollv2_0930.pdf}
\caption{PC chains for zmax = 30. Planck 2018 original lowE vs srollv2 likelihood (plik\_lite\_TTTEEE + lowl + simall\_EE vs plik\_lite\_TTTEEE + lowl + sroll2\_EE).
}
\label{fig:plot_taugtz_lowE_vs_srollv2}
\end{figure}

@@

>>>>

\begin{figure}[ht]
\includegraphics[width=0.45\textwidth]{paper/plots/pl18_taugtz_pc_zmax30_pl15_vs_pl18_simallEE_vs_pl18_srollv2.pdf}
\caption{Cumulative optical depth distributions from PC chains for zmax = 30 Planck 2015 vs 2018 simall\_EE vs 2018 srollv2 likelihood. 
}
\label{fig:plot_taugtz_2015_vs_2018_simallEE_vs_2018_srollv2}
\end{figure}

@@

% Notes:
% tau1 = (taulo + tauhi) --> (zre, xemin) --> xe(z) ==> tau2 ==> mjs --> tau3(mjs)
% taulo + tauhi = tau_desired
